\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}

\titleformat{\section}{\normalsize\bfseries\uppercase}{\thesection.}{0.6em}{}
\titlespacing*{\section}{0pt}{1.2em}{0.4em}

\title{Catering Services MoU — AEON 2025}
\date{}

\begin{document}
\begin{center}
{\Large\bfseries Catering Services MoU — AEON 2025}\\[0.6em]
\textit{Effective 2025-07-01}
\end{center}



\section*{Parties}
This Memorandum of Understanding (the ``Agreement'') is entered into as of 2025-07-01 between:
\begin{itemize}[leftmargin=1.2em]
\item \textbf{AEON Student Council} (``Engager''), an organisation, principal address PES University, 100 Feet Ring Road, BSK 3rd Stage, Bengaluru 560085, represented by Priya Sharma, President; and
\item \textbf{Spice Route Caterers Pvt. Ltd.} (``Vendor''), a corporation, principal address 12 MG Road, Bengaluru 560001, represented by Ramesh Gupta, Managing Director.
\end{itemize}

\section*{Recitals}
This Memorandum of Understanding is entered into as of 2025-07-01 between \textsc{AEON Student Council} (``\textsc{Engager}'') and \textsc{Spice Route Caterers Pvt. Ltd.} (``\textsc{Vendor}''). \textsc{Engager} is organizing the AEON 2025 event and requires professional catering services. \textsc{Vendor} has the expertise to provide these services and agrees to perform the work described in this agreement.

\textsc{Vendor} will provide full-service catering for the three-day AEON 2025 event. This includes comprehensive menu planning and a tasting session prior to the event, followed by complete meal service for all attendees on 2025-09-12, 2025-09-13, and 2025-09-14. \textsc{Vendor} is also responsible for the final cleanup of the venue kitchen facilities.

\section*{Definitions}
\begin{description}[leftmargin=1.5em,style=nextline]
  \item[\textsc{Services}] The catering and related services described in the Scope of Work.
  \item[\textsc{Deliverables}] The specific milestones and outputs listed in the Deliverables schedule, including menu plans and event-day services.
  \item[\textsc{Total Fee}] The total consideration of 750,000 INR payable for the Services.
  \item[\textsc{Effective Date}] 2025-07-01.
\end{description}

\section{Payment and Milestones}
\textsc{Engager} will pay \textsc{Vendor} a \textsc{Total Fee} of 750,000 INR according to the following schedule:
\begin{itemize}[leftmargin=1.2em]
\item \textbf{Deposit}: 30\% of the \textsc{Total Fee} (225,000 INR) due upon the execution of this agreement.
\item \textbf{Milestone Payments}: The remaining balance of 525,000 INR will be paid in installments upon the successful completion and acceptance of each \textsc{Deliverable}:
\begin{itemize}
\item Menu planning and tasting session: 10\% of balance.
\item Day 1 full catering service: 30\% of balance.
\item Day 2 full catering service: 30\% of balance.
\item Day 3 full catering service and cleanup: 30\% of balance.
\end{itemize}
\end{itemize}
All milestone payments are due within 15 days of the date of acceptance of the relevant \textsc{Deliverable}.
% PATTERN:payment-milestones

\section{Acceptance Criteria}
\textsc{Engager} will review each \textsc{Deliverable} within five (5) business days of receipt. If no written objection is received within this window, the \textsc{Deliverable} will be deemed accepted. If a \textsc{Deliverable} does not meet the agreed \textsc{Acceptance Criteria}, \textsc{Vendor} will have five (5) business days to remedy the deficiency at no additional cost to \textsc{Engager}.
% PATTERN:acceptance-window

\section{Indemnification}
Each party will indemnify and hold the other harmless from third-party claims arising from its performance under this agreement. This indemnity is capped at 750,000 INR. This cap does not apply to claims arising from gross negligence, willful misconduct, intellectual property infringement, or breach of confidentiality.
% PATTERN:indemnity-mutual-cap

\section{Limitation of Liability}
Neither party's total liability under this agreement will exceed 750,000 INR. Neither party is liable for indirect, consequential, or punitive damages. These limitations do not apply to the specific carve-outs identified in the indemnity clause.
% PATTERN:liability-cap

\section{Termination}
\textsc{Engager} or \textsc{Vendor} may terminate this agreement for convenience by providing 30 days' written notice to the other party. Either party may terminate this agreement for cause if the other party fails to cure a material breach within 7 days of receiving written notice of such breach.
% PATTERN:termination-dual

\section{Force Majeure}
Neither party is liable for delays or failures in performance caused by events beyond their reasonable control, including pandemics, cyberattacks, government actions, supply-chain disruptions, or infrastructure outages. This clause excuses performance but does not excuse the obligation to pay for services already rendered and accepted.
% PATTERN:force-majeure-carveouts

\section{Confidentiality}
The parties will maintain the confidentiality of all non-public information shared during this engagement. This obligation survives the termination or expiration of this agreement for a period of 2 years.
% PATTERN:confidentiality-survival

\section{Subcontracting}
\textsc{Vendor} will not subcontract any portion of the \textsc{Services} without the prior written consent of \textsc{Engager}. \textsc{Vendor} remains fully responsible for the performance and conduct of any approved subcontractors.
% PATTERN:no-subcontract-consent

\section{Insurance Requirements}
\textsc{Vendor} will maintain general liability insurance of at least 1,000,000 INR and professional indemnity insurance of at least 500,000 INR. \textsc{Engager} must be named as an additional insured on these policies. \textsc{Vendor} will provide certificates of insurance upon request.
% PATTERN:insurance-named-insured

\section{Modifications}
Any modification or amendment to this agreement must be made in a written instrument signed by authorized signatories of both parties. No oral agreements or course-of-conduct changes will be valid.
% PATTERN:modifications-in-writing

\section{Governing Law and Dispute Resolution}
14.1 Governing Law. This agreement is governed by the laws of Karnataka, India.
14.2 Dispute Resolution. Any disputes arising under this agreement will be resolved first through mediation, and if unsuccessful, through binding arbitration in Bengaluru.
14.3 Severability. If any provision of this agreement is held to be invalid or unenforceable, the remaining provisions will continue in full force.
14.4 Entire Agreement. This document constitutes the entire agreement between the parties regarding its subject matter.
14.5 Counterparts. This agreement may be executed in counterparts, including by electronic signature.
% PATTERN:governing-law-venue-severability

\section{Publicity Restrictions}
\textsc{Vendor} will not use \textsc{Engager}'s name, logo, or the AEON 2025 event identity in any marketing, advertising, or promotional materials without the prior written consent of \textsc{Engager}.
% PATTERN:no-publicity


\section*{Signatures}
\vspace{2em}
\noindent\begin{minipage}[t]{0.45\textwidth}
\textbf{Engager}\\[2em]
\rule{\linewidth}{0.4pt}\\
Name: Priya Sharma\\
Title: President\\
For: AEON Student Council\\
Date: \rule{6em}{0.4pt}
\end{minipage}\hfill
\noindent\begin{minipage}[t]{0.45\textwidth}
\textbf{Vendor}\\[2em]
\rule{\linewidth}{0.4pt}\\
Name: Ramesh Gupta\\
Title: Managing Director\\
For: Spice Route Caterers Pvt. Ltd.\\
Date: \rule{6em}{0.4pt}
\end{minipage}

\vfill
\noindent\hrulefill\\[0.4em]
{\footnotesize\textit{This draft is a starting point produced by software. It is not legal advice. Have it reviewed by a qualified attorney in your jurisdiction before signing.}}

\end{document}
